SPARQL on the Open, Decentralised Web

### 2016-08-03 dissertation/introdefhistory.tex
add todo
remove todo
Big Problem statement #7

The introduction provided a very basic view of the technology, this
chapter will further discuss some important aspects of the Semantic
Web, as it provides guidance for the investigation detailed in the
papers.

As such, the following serves to tie the published papers into a
whole, provide an overarching rationale and problem statements,
overview of the contributions and a discussion of the problematic
sides of the study seen from a philosophy of science viewpoint. It is
structured as follows: Section~\ref{sec:nodef} discusses the
possibility of defining the Semantic Web,
Section~\ref{sec:objectivity} discusses the problem of maintaining
objectivity, Section~\ref{sec:history} attempts to satisfy the
previous discussion by detailing the author's personal involvement in
the Semantic Web. Section~\ref{sec:motivation} has an overview of the
motivation behind this work.  Section~\ref{sec:prelims} provides some
further technical details and Section~\ref{sec:related} puts the
present work into the context within the existing
literature. Section~\ref{sec:problems} summarises important research
problems and details the motivation.
Sections~\ref{sec:papersincontext}~and~\ref{sec:unpublished} details
how the contributions address these problems and discusses weaknesses
of the papers with the benefit of hindsight. Future work is discussed
in Section~\ref{sec:future}. Key insights are finally summarised in
Section~\ref{sec:conclusions}.\todo{Big problem statement here}

>>>>

The introduction provided a very basic view of the technology, this
chapter will further discuss some important aspects of the Semantic
Web, as it provides guidance for the investigation detailed in the
papers. The overarching problem this work tries to address is this:

\begin{quote}
To achieve a Semantic Web where anyone can say anything about
anything, and where everyone is enabled to analyse data that have been
contributed, there is a difficult balance between centralising
infrastructure and decentralising it, and between processing on
clients and servers.
\end{quote}

As such, the following serves to tie the published papers into a
whole, provide an overarching rationale and problem statements,
overview of the contributions and a discussion of the problematic
sides of the study seen from a philosophy of science viewpoint. It is
structured as follows: Section~\ref{sec:nodef} discusses the
possibility of defining the Semantic Web,
Section~\ref{sec:objectivity} discusses the problem of maintaining
objectivity, Section~\ref{sec:history} attempts to satisfy the
previous discussion by detailing the author's personal involvement in
the Semantic Web. Section~\ref{sec:motivation} has an overview of the
motivation behind this work.  Section~\ref{sec:prelims} provides some
further technical details and Section~\ref{sec:related} puts the
present work into the context within the existing
literature. Section~\ref{sec:problems} summarises important research
problems and details the motivation.
Sections~\ref{sec:papersincontext}~and~\ref{sec:unpublished} details
how the contributions address these problems and discusses weaknesses
of the papers with the benefit of hindsight. Future work is discussed
in Section~\ref{sec:future}. Key insights are finally summarised in
Section~\ref{sec:conclusions}.
